Significance testing with forward stepwise and grouped forward stepwise model selection

### 2013-09-28 paper/paper.tex
Made a larger model selection simulation

\begin{figure}
\begin{center}
\subfigure[Gaussian design]{
\label{fig:lassopvala}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_gaussian_design.pdf}}
\hspace{-15pt}
\subfigure[Categorical design]{
\label{fig:lassopvalb}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_categorical_design.pdf}}
\caption{\small \it The left panel shows results of a simulation with
  an independent Gaussian design matrix and a signal vector having
  three groups with non-zero coefficients of sizes one, two, and
  three, and seven groups of noise variables with sizes varying from
  one to ten, for a total of 30 variables. For the right panel we
  repeated this setup, but group sizes corresponded to levels of
  categorical variables. The groups of size one were increased to two,
so there are 10 categorical variables with a total of 32 levels.}
\end{center}
\end{figure}

\label{fig:smallselection}

@@

>>>>

\begin{figure}
\begin{center}
\subfigure[Gaussian design]{
\label{fig:lassopvala}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_gaussian_design.pdf}}
\subfigure[Large Gaussian design]{
\label{fig:lassopvala}
\includegraphics[width=0.5\textwidth]{../figs/large_sim_gaussian_design.pdf}}
%\hspace{-15pt}
\subfigure[Categorical design]{
\label{fig:lassopvalb}
\includegraphics[width=0.5\textwidth]{../figs/small_sim_categorical_design.pdf}}
\caption{\small \it The left panel shows results of a simulation with
  an independent Gaussian design matrix and a signal vector having
  three groups with non-zero coefficients of sizes one, two, and
  three, and seven groups of noise variables with sizes varying from
  one to ten, for a total of 30 variables. For the right panel we
  repeated this setup, but group sizes corresponded to levels of
  categorical variables. The groups of size one were increased to two,
so there are 10 categorical variables with a total of 32 levels.}
\end{center}
\end{figure}

@@

\input{../selection_sim_results.tex}

The large simulation has 50 groups, 25 of size 1, 10 of size 5, 10 of
size 10, and 5 of size 15. Signal vectors were supported on random
choices of 10 of these groups (changing in each realization), with
non-zero signal magnitude around $\sqrt{2\log p}$ where $p = 250$
(roughly 3.3). The design matrix had 200 rows and the simulation
performed 100 realizations.
